Calendar-based graphics for visualising people's daily schedules

### 2017-07-12 main.Rmd
Init writing for lag scatterplot

The nighttime events, such as White Night and New Year Evening Firework, has barely affected the operation of Flagstaff Station but heavily affected the incoming traffic to Flinders Street Station and State Library on these days.

@@

```{r scatterplot, fig.height = 5, fig.cap = "Lag scatterplot in the daily calendar. Lagged hourly counts are plotted against current ones to demonstrate the autocorrelation at the order of 1. The positive association between the one-hour-ahead count and the present regardless of the data values takes place on non-working days."}
```

The newly computed coordinates not only work with the simple geoms such as lines and points, but also boxplot and other complex geoms. Figure \ref{fig:boxplot} uses the side-by-side boxplots with the loess smooth line superimposed as an example. It shows the distribution of hourly counts across all the 43 sensors.

@@

In general, unimodality features the non-work days whereas bimodality on work days. The last week of December is just the holiday season: people are off work on the day before Christmas, go shopping on the Boxing day, and hanging out for the firework in the New Year Evening.

>>>>

The nighttime events, such as White Night and New Year Evening Firework, has barely affected the operation of Flagstaff Station but heavily affected the incoming and outgoing traffic to Flinders Street Station and State Library on these days.

@@

The \code{frame_calendar} does not constrain itself to mapping only temporal variable to the \code{x}. Figure \ref{fig:scatterplot} shows the lag scatterplot where hourly counts are assigned to the \code{x} and lagged themselves to the \code{y}. It provides a visual tool for identifying repeating patterns.

```{r scatterplot, fig.height = 5, fig.cap = "Lag scatterplot in the daily calendar. Lagged hourly counts are plotted against current ones to demonstrate the autocorrelation at lag 1. The correlation between them is more consitent on non-work days than work days."}
```

The newly computed coordinates not only work with the simple geoms such as lines and points, but also boxplot and other complex geoms. Figure \ref{fig:boxplot} uses the side-by-side boxplots with the loess smooth line superimposed as an example. It shows the distribution of hourly counts across all the 43 sensors. In general, bimodality features work days whereas unimodality features the rest of the days. The last week of December is just the holiday season: people are off work on the day before Christmas, go shopping on the Boxing day, and hanging out for the firework in the New Year Evening.

@@

### 2017-07-12 main.tex
Init writing for lag scatterplot

@@

\caption[Lag scatterplot in the daily calendar]{Lag scatterplot in the daily calendar. Lagged hourly counts are plotted against current ones to demonstrate the autocorrelation at the order of 1. The positive association between the one-hour-ahead count and the present regardless of the data values takes place on non-working days.}\label{fig:scatterplot}
\end{figure}
\end{CodeChunk}

The newly computed coordinates not only work with the simple geoms such
as lines and points, but also boxplot and other complex geoms. Figure
\ref{fig:boxplot} uses the side-by-side boxplots with the loess smooth
line superimposed as an example. It shows the distribution of hourly
counts across all the 43 sensors.

>>>>

The \code{frame_calendar} does not constrain itself to mapping only
temporal variable to the \code{x}. Figure \ref{fig:scatterplot} shows
the lag scatterplot where hourly counts are assigned to the \code{x} and
lagged themselves to the \code{y}. It provides a visual tool for
identifying repeating patterns.

@@

\caption[Lag scatterplot in the daily calendar]{Lag scatterplot in the daily calendar. Lagged hourly counts are plotted against current ones to demonstrate the autocorrelation at lag 1. The correlation between them is more consitent on non-work days than work days.}\label{fig:scatterplot}
\end{figure}
\end{CodeChunk}

The newly computed coordinates not only work with the simple geoms such
as lines and points, but also boxplot and other complex geoms. Figure
\ref{fig:boxplot} uses the side-by-side boxplots with the loess smooth
line superimposed as an example. It shows the distribution of hourly
counts across all the 43 sensors. In general, bimodality features work
days whereas unimodality features the rest of the days. The last week of
December is just the holiday season: people are off work on the day
before Christmas, go shopping on the Boxing day, and hanging out for the
firework in the New Year Evening.
